Supplemental Materials for the paper: \\Pesticides pollution of small streams in Germany

### 2016-08-10 article.tex
added model to TU.

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We used the number of samplings ($n_i$) as an offset to account different sampling efforts. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$).
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $log(TU_{max})$ (see Supplement for details). \todo{TRUE?}
GAM were fitted using the mgcv package \citep{wood_fast_2011}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure xxx).}
  \label{fig:figvar}
\end{figure}
\todo{prettify figure!}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant increases.
  }
  \label{fig:figrac}
\end{figure}

>>>>

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$) and used the number of sampling events per site ($n_i$) as an offset to account different sampling efforts. 
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $TU_{max}$ (see Supplement). 
We used pointwise 95\% Confidence Intervals of the first derivative of the fitted smooth to check if there are regions of statistically significant changes.
GAMs were fitted using the mgcv package \citep{wood_fast_2011}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure xxx).}
  \label{fig:figvar}
\end{figure}
\todo{prettify figure! check cowplot package.}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant increases. Dashed lines denote 95\% Confidence Intervals.
  }
  \label{fig:figrac}
\end{figure}

### 2016-08-10 supplement/Supplemental_Materials.tex
added model to TU.

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{data_cleaning}
	\caption{Overview on data cleaning steps. After cleaning data has been stored in a relational spatial PostgreSQL database.}
	\label{fig:data_cleaning}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{varclus}
	\caption{Complete Linkage Cluster Dendrogram of Jaccard Similarity of analysed compound spectra between federal states. Abbreviations of state names according to ISO 3166-2:DE.}
	\label{fig:varclus}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.75\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{ezgagrirac}
	\caption{Raw data used for the model in equation xxx and Figure xxx of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey points are sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}
\todo{update refs}

>>>>

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}
\usepackage{amsmath}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{data_cleaning}
	\caption{Overview on data cleaning steps. After cleaning data has been stored in a relational spatial PostgreSQL database.}
	\label{fig:data_cleaning}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{varclus}
	\caption{Complete Linkage Cluster Dendrogram of Jaccard Similarity of analysed compound spectra between federal states. Abbreviations of state names according to ISO 3166-2:DE.}
	\label{fig:varclus}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.75\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

@@

\section{RAC Exceedances}
\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{ezgagrirac}
	\caption{Raw data used for the model in equation xxx and Figure xxx of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey points are sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}
\todo{update refs}

\pagebreak
\section{Toxic Units}

We modeled the 95th percentile of $TU_{max}$ on a logarithmic scale assuming a Normal distribution:

\begin{align}
\begin{split}
  log(TU_{max}) \sim Normal(\mu_i, \sigma) \\
  log(\mu_i)= \beta_0 + f_1(Agri_i) + f_2(Size_i)
\end{split}
\end{align}

where $TU_{max i}$ is 95th percentile of $TU_{max}$ at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site.  
$f_1$ and $f_2$ are smoothing functions.

Because of samples at low polluted sites contained only values below the limit of quantification (LOQ) the derived $TU_{max}$ were also left censored (at a value of $10^{-8.75}$), thus we have

\begin{align}
  log(TU_{max~i})=\begin{cases}
    \beta_0 + f_1(Agri_i) + f_2(Size_i) + \epsilon_i, & \text{if $log(TU_{max}) > -8.75 $}\\
    -8.75, & \text{if $log(TU_{max}) \le -8.75 $}.
  \end{cases}
\end{align}

Instead of assuming a fixed value for the data \textless LOQ, we use a model taking this censoring into account \citep{helsel_fabricating_2006} with the expected value being a mixture of censored and uncensored data.

\begin{align}
\begin{split}
	E(y_i | x_i) = P(uncensored|x_i) \times E(y_i | y_i > -8.75)) + P(censored|x_i) \times -8.75\\
	Var(y_i) = \sigma
\end{split}
\end{align}

With $y_i$ being $log(TU_{max~i})$ and $x_i$ the predictor functions $f_1(Agri_i) + f_2(Size_i)$. $P(censored|x_i)$ is the probability of censoring at given predictors. Further, we assumed constant variance. This model was fitted using the gamlss packages \citep{stasinopoulos_generalized_2007}.

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{ezgagritu}
	\caption{Raw data of effect of agriculture and catchment size on the 95th percentile of log(TUmax).}
	\label{fig:ezgagritu}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.9\textwidth]{ezgagritumodel}
	\caption{Effect of agriculture within the catchment (left) and catchment size (rigth) on the 95th percentile of log(TUmax). The model took censored data into account (see description above). Dashed lines denote 95\% Confidence Intervals.}
	\label{fig:ezgagritu_model}
\end{figure}
